Fully Generalized Compilation

### 2017-02-05 papers/paper.tex
Adds basic compiler diagram

@@

\section{Methods}
\subsection{Grammars}
\subsection{Constructors}
\subsection{AST Transformations}

\section{Results}
\subsection{Quicksort Cython Comparison}
This is not meant to be a robust benchmark. Instead, it aims to show that Cython and Transpilation yield similar results.

>>>>

% Package for flowcharts/diagrams

\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}

\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]
\tikzstyle{io} = [rectangle, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=blue!30]
\tikzstyle{process} = [diamond, minimum width=2cm, minimum height=0cm, text centered, draw=black, fill=orange!30]
\tikzstyle{arrow} = [thick,->,>=stealth]

% ==================================================
% Begin Paper
% ==================================================

@@

\section{Methods}

\subsection{Grammars}
\subsection{Constructors}
\subsection{AST Transformations}

\newpage

\begin{tikzpicture}[node distance=2.5cm]

    \node (sourcea) [startstop]                 {Source Code A};
    \node (lexer)   [process, below of=sourcea] {Lexical Analyzer};
    \node (tokens)  [io, below of=lexer]        {Symbolic Tokens};
    \node (parser)  [process, below of=tokens]  {Parser};
    \node (asta)    [io, below of=parser]       {AST};
    \node (trans)   [process, below of=asta]    {Transformer};
    \node (astb)    [io, below of=trans]        {Intermediate AST};
    \node (gen)     [process, below of=astb]    {Generator};
    \node (stop)    [startstop, below of=gen]   {Source Code B};

    \draw [arrow] (sourcea) -- (lexer);
    \draw [arrow] (lexer) -- (tokens);
    \draw [arrow] (tokens) -- (parser);
    \draw [arrow] (parser) -- (asta);
    \draw [arrow] (asta) -- (trans);
    \draw [arrow] (trans) -- (astb);
    \draw [arrow] (astb) -- (gen);
    \draw [arrow] (gen) -- (stop);

\end{tikzpicture}

\section{Results}
\subsection{Quicksort Cython Comparison}

This is not meant to be a robust benchmark. Instead, it aims to show that Cython and Transpilation yield similar results.
